---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# remice <a href="https://erictong2.github.io/remice"><img src="man/figures/logo.svg" align="right" height="139" alt="remice website" /></a>

Have your collaborators been remiss in their data collection? 

Have you experienced characters in your numeric columns? 

Do rows ever get incorrectly entered or swapped? 

The overarching goal of the remice package is to account for remiss data, providing a way to identify and solve those problems. 

## Installation

You can install the development version of remice like so:

```{r, eval = FALSE}
install_github("erictong2/remice")
```

If you prefer, you can also go to the Github website (https://github.com/EricTong2/remice/) and download the package from there.

## Function List
These are the functions included in the package: 

* `analyze_type()` takes a column of characters and determines if any values in that row are not of a specified type. While this does not directly fix the types of the data, it creates a table to highlight areas in which the data could cause errors for other functions, allowing for those rows to be manually fixed. 

* `table_different()` takes a column of characters and creates a table of strings that are uncommonly found in a dataset. This is aimed to mitigate various typos found by either entering data or from survey responses. For example, if all of the column values are "True" except for a single "Ture", it is likely for a typo to have occurred. This function does not fix any problems, but it highlights the row numbers where the data should be checked. 

* `separate_list()` takes a column of characters and creates a table of the most common responses when multiple responses could exist in one row. For example, if two of the responses are "Apple, Banana, and Orange" and "Banana, Orange", this would output a table of "Apple: 1, Banana: 2, Orange: 2." This can be used on a survey about comfort foods, where a response might be 

* `plot_outliers()` takes multiple columns of numeric data that was longitudinally collected and checks for any abnormally large changes in the data. This could be used to check for potential outliers or areas where the data was mis-input: for example, recording "11" grams instead of "21" grams. In addition, the user inputs a percent change, and any points that have a change greater than the input for any two points would be plotted in a graph. 

## Data List

* `food_data` is a list of 

## Example

This is an example of `separate_list()` using the Comfort Food column from `food_data`

```{r example1}
library(remice)

separate_list(food_data, "comfort_food", 5)
```

This is an example of `plot_outliers()` using the `mouse_data_bw_clean` dataset:

```{r example2}
library(remice)

table_different(mouse_data_birth, "Treatment")
```
