---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# remice <a href="https://erictong2.github.io/remice"><img src="man/figures/logo.svg" align="right" height="139" alt="remice website" /></a>



Have your collaborators been remiss in their data collection? Have you experienced characters in your numeric columns? Do rows ever get incorrectly entered or swapped? Remice aims to provide a way to identify and solve those problems. 

The overarching goal of the remice package is to account for remiss data. 

## Installation

You can install the development version of remice like so:

```{r}
install_github("erictong2/remice")
```

## Function List
These are the functions included in the package: 

* `analyze_type()` takes a column and determines if any values in that row are not of a specified type, which could cause errors for other functions

* `table_different()` creates a table of strings that are uncommonly found

* `separate_list()` creates a table of the most common responses, when multiple responses could exist in one row. 
    For example, this could be used on a survey about comfort foods, where a response might be ""
    -plot_outliers uses longitunial data and checks for any abnormally large changes in the data. The user inputs a percent change, and any points above that will be plotted. 

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(remice)


```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.

You can also embed plots, for example:


In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
