---
title: "remice"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{remice}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
favicon: "../man/figures/logo.png"
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "../man/figures/",
  out.width = "100%"
)
```
<link rel="icon" type="image/png" href="../man/figures/logo.png">


# Overview

The remice package provides tools to help clean and analyze datasets, especially those related to mice experiments. It simplifies tasks such as type validation, identifying uncommon strings, summarizing list-like columns, and detecting outliers in longitudinal data.

This vignette introduces the main functions of remice and provides examples of their usage.

---

# Installation

To install the development version of remice from GitHub, run:

```{r, eval = FALSE}
devtools::install_github("erictong2/remice")
```

Or if you have the source code:
```{r, eval = TRUE}
library(remice)
```

---

# Key Functions

## `analyze_type`

Use `analyze_type` to check whether all values in a column match the specified type. Here, we check if `Body Weight 1` contains numeric values.

```{r analyze-type-example}
analyze_type(mouse_data_bw_dirty, "Body Weight 1", "numeric")
```

---

## `table_different`

The `table_different` function identifies strings that appear less frequently in a column. Let’s analyze the `Comfort Foods` column:

```{r table-different-example}
table_different(mouse_data_birth, "Treatment", frequency = 2)
```

---

## `separate_list`

When multiple responses exist in one row, use `separate_list` to generate a table of the most common responses. For example:

```{r separate-list-example}
separate_list(food_data, "comfort_food", min_frequency = 10)
```

---

## `plot_outliers`

The `plot_outliers` function visualizes rows with unusually large changes based on a specified percent threshold. Here’s how to use it:

```{r plot-outliers-example}
plot_outliers(mouse_data_bw_clean, c("Body Weight 1", "Body Weight 2", "Body Weight 3"), threshold = 0.2)
```

---

# Conclusion

The `remice` package simplifies data cleaning and analysis for datasets related to mice experiments. Use it to validate data types, summarize columns, identify outliers, and more.

For more details, refer to the function documentation:

```{r, eval = FALSE}
?remice
```

---
