---
title: "remice"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{remice}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
favicon: "../man/figures/logo.png"
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "../man/figures/",
  out.width = "100%"
)
```
<link rel="icon" type="image/png" href="../man/figures/logo.png">
```{r, echo = FALSE}
library(remice)
```


# Overview

The remice package provides tools to help clean and analyze datasets, especially those related to mice experiments. 

This vignette will provide more detailed examples for each of the functions, including the parameters and edge cases. 

For additional information about the functions or data sets, refer to the README file. 

---

#Function Examples

## `analyze_type`

`analyze_type` is used to check whether all values in a column (`Body Weight 1`) match the specified type (`numeric`). 

```{r analyze-type-example}
analyze_type(mouse_data_bw_dirty, "Body Weight 3", "numeric")
```

`analyze_type` will automatically fail if the column name does not exist or if the data type inputted is inaccurate

```{r, error=TRUE}
analyze_type(mouse_data_bw_dirty, "Body Weight 1", "int")
```
```{r, error=TRUE}
analyze_type(mouse_data_bw_dirty, "Date", "integer")
```

Note that this will fail to find the value "13.5" if checking for character values, as 13.5 can be cast to a character. 
---

## `table_different`

The `table_different` function identifies strings that appear less frequently in a column.

```{r}
table_different(mouse_data_birth, "Treatment", frequency = 2)
```

Note that this function is built for character values, so non-character columns will produce an error

```{r, error = TRUE}
table_different(mouse_data_bw_clean, "Body Weight 1")
```

This function is not adivsed to be used on columns with a large amount of differing values, as the results will be messy.

```{r}
table_different(mouse_data_birth, "ID")
```


---

## `separate_list`

When multiple responses exist in one row, use `separate_list` to generate a table of the most common responses. For example:

```{r}
separate_list(food_data, "comfort_food", min_frequency = 10)
```

Again, `separate_list` should be used on character columns, and non-character values will provide an error
```{r, error = TRUE}
separate_list(mouse_data_bw_clean, "Body Weight 1")
```


---

## `plot_outliers`

The `plot_outliers` function visualizes rows with unusually large changes based on a specified percent threshold.

```{r}
plot_outliers(mouse_data_bw_clean, c("Body Weight 1", "Body Weight 2", "Body Weight 3"), threshold = 0.2)
```

All of the columns must be numeric, and rows with NA values can either be ignored or give an error.

```{r, error = TRUE}
plot_outliers(mouse_data_bw_dirty, c("Body Weight 1", "Body Weight 2", "Body Weight 3"))
```


---
